Molecular dynamics simulation of synchronization in driven particles

### 2021-01-04 manuscript/manuscript_ajp_2020.tex
moved discussion of colloid interactions to chain section

Complex environments can be
engineered with light by %, typically made 
using diffraction gratings to create a patterned
potential energy landscape 
with one or more laser beams \cite{}.
%

@@

We confine the particles using a position dependent 
potential energy function, called a landscape or substrate.
 %The landscape potential energy $U(\vec{r})$ is static 
 %with fixed minima and maxima
 %that are periodic or quasi-periodic,
 %as described in Sec.~\ref{sec:results}.
% 
The landscape is modulated in the y-direction
with the periodic function 
%% %that used in Sec.~\ref{sec:one}
% where 
 \begin{equation}
   U(y) = U_0 \cos{(N_p \pi y / L)}
     \label{eq:ysubstrate}
\end{equation}
 where $N_p$ are the number of periods,
 % $L$ is the period length,
 and $U_0$ is an adjustable parameter
 to set the depth of the minima
 with simulation units of energy $E_0 = 1$. 
 %We define the substrate strength to be
 %the maximum force the substrate can exert on a particle 
 %$A_p = 2\pi U_0/L$.
 %
 We plot this function in 
 Fig.~\ref{fig:landscape0}
 we use $N_p = 3$ to illustrate the features of
 Eq.~\ref{eq:ysubstrate}.
 In Fig.~\ref{fig:landscape0}(a) we show 
 the $x-y$ plane with a contour plot
 of the the 2D potential energy landscape,
 where 
 the maxima are colored red and the minima colored blue.
 The confining force on a particle $i$
 %arises from a potential function 
 %creating a landscape of potential minima and maxima
 %that modify the force on a particle as a function of position
 is calculated as 
 $\vec{F}^{l}_i(\vec{r}_i) = -\nabla U_l(\vec{r}_i)$.
 In Fig.~\ref{fig:landscape0}(b) we plot the function
 $U(y)$ to illustrate how the magnitude
 $\vec{F}^{l}_i$ is calculated from particle position $y_i$.  
 %in the $y-$direction.

>>>>

@@

We confine the particles using a position dependent 
potential energy function, called a landscape or substrate.
 %The landscape potential energy $U(\vec{r})$ is static 
 %with fixed minima and maxima
 %that are periodic or quasi-periodic,
 %as described in Sec.~\ref{sec:results}.
% 
The landscape is modulated in the y-direction
with the periodic function 
%% %that used in Sec.~\ref{sec:one}
% where 
 \begin{equation}
   U(y) = U_0 \cos{(N_p \pi y / L)}
     \label{eq:ysubstrate}
\end{equation}
 where $N_p$ are the number of periods,
 % $L$ is the period length,
 and $U_0$ is an adjustable parameter
 to set the depth of the minima
 with simulation units of energy $E_0 = 1$. 
 %We define the substrate strength to be
 %the maximum force the substrate can exert on a particle 
 %$A_p = 2\pi U_0/L$.
 %
 In experiment 
 complex environments can be
 engineered with light by %, typically made 
 using diffraction gratings to create a patterned
 potential energy landscape 
 with one or more laser beams \cite{}.
 %
 We plot this function in 
 Fig.~\ref{fig:landscape0}
 we use $N_p = 3$ to illustrate the features of
 Eq.~\ref{eq:ysubstrate}.
 In Fig.~\ref{fig:landscape0}(a) we show 
 the $x-y$ plane with a contour plot
 of the the 2D potential energy landscape,
 where 
 the maxima are colored red and the minima colored blue.
 The confining force on a particle $i$
 %arises from a potential function 
 %creating a landscape of potential minima and maxima
 %that modify the force on a particle as a function of position
 is calculated as 
 $\vec{F}^{l}_i(\vec{r}_i) = -\nabla U_l(\vec{r}_i)$.
 In Fig.~\ref{fig:landscape0}(b) we plot the function
 $U(y)$ to illustrate how the magnitude
 $\vec{F}^{l}_i$ is calculated from particle position $y_i$.  
 %in the $y-$direction.
